%-------------------------
% Courtesy of Sourabh Bajaj (https://github.com/sb2nov/resume)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
%\fancyhead[LE,RO]{Right Text}
%\fancyhead[RE,LO]{Left Text}
\fancyfoot[LE,LO]{\fontsize{8}{10}\selectfont\today}
%\fancyfoot[LE,RO]{\thepage}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeText}[1]{
  \item\small{
    \textrm{#1}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/mfathirirhas/}{\Large Muhammad Fathir Irhas}} & Email : \href{mailto:fathir.irhas@outlook.com}{fathir.irhas@outlook.com}\\
  Software Engineer & Mobile/Whatsapp : +62-812-2444-1284 \\
  Jakarta and Bandung & Linkedin: \href{https://linkedin.com/in/mfathirirhas}{linkedin.com/in/mfathirirhas} 
\end{tabular*}

\section{Summary}  
  {
    \it Software Engineer experienced in backend development using several technologies included Go, Java, Rust, and other tools related.
    Having experiences working in microservices architecture communicating eachother through APIs in form of HTTP/REST, gRPC, GraphQL, and message queue. 
    Handling projects and features development, maintaining, and monitoring. Able to work individually or in team. 
    Focus on correctness of works and optimize for speeds. 
    Adaptable and learnability, might not knowing some techs, but with enough fundamentals able to learn and implement it. Willing to explore even tech with steep learning curve like Rust.
  }

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universitas Telkom}{Bandung, Indonesia}
      {Sarjana Komputer (\textit{Bachelor degree in Computer Science})}{2012 -- 2016}
  \resumeSubHeadingListEnd


% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Lifepal}{Jakarta}
    {Backend Engineer}{May 2022 - Oct 2022}
    \resumeItemListStart
      \resumeText
        {Working on telesales team on their telesales app in Rust.}
      \resumeItem{Tech Stacks}
        {Rust, Tokio, Go, KubeMQ, Redis, Postgresql}
    \resumeItemListEnd

    \resumeSubheading
      {Tiket.com}{Jakarta}
      {Backend Engineer}{November 2020 - December 2021}
      \resumeItemListStart
        \resumeItem{Team}
          {Flight Prepurchase}
        \resumeItem{Tech Stacks}
          {Go, Java Spring, MongoDB, Redis, Kafka, RabbitMQ, etc.}
        \resumeItem{Project}
          {Creating internal mock server for mocking part of inter-services communications, especially partner and integration with flight supplier.}
        \resumeText
          {Working on flight search caching tools to populate search cache preemptively for promos purpose.}
      \resumeItemListEnd

    \resumeSubheading
      {Tokopedia}{Jakarta}
      {Software Engineer}{July 2018 - April 2020}
      \resumeItemListStart
        \resumeItem{Team}{Fintech}
        \resumeItem{Tech Stacks}
          {Golang, Javascript, PostgreSQL, MySQL, Redis, NSQ, gRPC, and GQL.}
        \resumeItem{Saldo Tokopedia}
          {Handling Saldo Service as journaling every transactions in Tokopedia}
          \resumeItemListStart
            \resumeText{Design and implements transactions code for every products and services by storing them in service's local cache refreshed every n minutes using goroutine background process.}
            \resumeText{Handling Saldo Service internal dashboard.}
            \resumeText{Migrate old code from Perl related to saldo service into Golang.}
            \resumeText{Help other teams and services to integrate into Saldo Service.}
            \resumeText{Saldo buyer and seller separatations, refactoring APIs to adjust saldo separations, along with its grpc and gql apis.}
            \resumeText{Saldo buyer and seller separatations, revamping saldo's monolith service along with its front end in Golang template with javascript(jquery) frontend}
            \resumeText{Refactor codes for unit tests coverage, adding testability to the code.}
            \resumeText{Data query for specific data fetching and changes not covered by service's api and internal dashboard.}
          \resumeItemListEnd
        \resumeItem{Internal Dashboard}
          {Work on internal dashboard as backoffice to business and ops teams.}
        \resumeItem{EGold}
          {Create  datadog monitoring dashboard for Tokopedia Emas buy and sell success, attempts rate and collect error reporting in the dashboard.}
        \resumeItem{Monitoring}
          {Monitor services running through server's logs, grafana and datadog dashboard.}
        \resumeItem{Support}
          {Support other teams to integrate. Support ops teams relating issues from customers.}
      \resumeItemListEnd

    \resumeSubheading
      {Anabatic}{Serpong, Tangerang}
      {Software Engineer/Technical Consultant}{Nov 2016 - Jun 2018}
      \resumeItemListStart
        \resumeItem{Tech Stacks}
          {Java(Spring), PHP(Codeigniter), MySQL, Javascript.}
        \resumeItem{Emporia Digital Raya}
          {Subsidiary of Anabatic. Worked on Eksporaja, a product as a channel partner with Alibaba for exporter in Indonesia. Maintain Emporia main website. Worked on Udaily another product from emporia for apartment cluster management and daily stuffs.}
        \resumeItem{Anabatic}
          {Worked on client site. Supporting development in Allianz.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      {Backend Development using Golang, Rust and few Java}
    }
    \item{
      {Databases with Postgresql, Mysql, SQLite, and Mongodb}
    }
    \item{
      {In-memory cache with Redis}
    }
    \item{
      {API with HTTP, gRPC, GraphQL, Message Queue.}
    }
    \item{
      {Some design patterns required in software developments.}
    }
    \item{
      {Maintaining and Debugging.}
    }
    \item{
      {Unit Testing and Integration Testing.}
    }
    \item{
      {Benchmarking and Monitoring.}
    }
    \item{
      {...and others related.}
    }
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Links}
  \resumeSubHeadingListStart
    \resumeSubItem{Github}
      {\href{https://github.com/mfathirirhas}{https://github.com/mfathirirhas}}
    \resumeSubItem{Rust Note - notes I take while learning Rust}
      {\href{https://mfathirirhas.github.io/rust-note}{https://mfathirirhas.github.io/rust-note}}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}