\cvsection{Experience}
\begin{cventries}

\cventry
    {Backend Engineer}
    {Tiket.com}
    {Jakarta, Indonesia}
    {Nov 2020 - Present}
    {
        \begin{cvitems}
            \item {Working in Flight Prepurchase team.}
            \item {Tech stacks: Go, Java Spring, MongoDB, Redis, Kafka, RabbitMQ, etc.}
            \item {Creating internal mock server for mocking part of inter-services communications, especially partner and integration with flight supplier.}
            \item {Working on flight search caching tools to populate search cache preemptively}
        \end{cvitems}
    }

\cventry
    {Software Engineer}
    {Tokopedia}
    {Jakarta, Indonesia}
    {Jul 2018 - April 2020}
    {
        \begin{cvitems}
            \item {Use Golang, Javascript, PostgreSQL, MySQL, Redis, NSQ, gRPC, and GQL.}
            \item {Contribute in Saldo Tokopedia, Internal Tools, and some investment products.}
            \item {Contribute in Saldo Tokopedia Saldo Penghasilan separation.}
            \item {Revamp Saldo Tokopedia legacy front end.}
            \item {Rewrite Saldo Tokopedia legacy codebase to implement interface based development and creating testable code.}
            \item {Implement unit tests.}
            \item {Develop services doing CRUD in PostgreSQL and MySQL as persistence and Redis as cache.}
            \item {Develop APIs in REST, gRPC, and GQL.}
            \item {Develop message queue using NSQ.}
            \item {Develop cron for task scheduling.}
            \item {Create EGold(Tokopedia Emas) metrics monitoring in datadog.}
            \item {Monitor services from datadog, prometheus, and server log.}
            \item {Collaborate with other team to provide interface and integration to/from Fintech’s products/services.}
            \item {Migrate some legacy internal API from Perl to Golang.}
            \item {Execute tickets coming from users through ops team relating to issues in products.}
        \end{cvitems}
    }

\cventry
    {Technical Consultant}
    {Anabatic Technologies}
    {Serpong Tangerang, Indonesia}
    {Jan 2018 - Jun 2018}
    {
        \begin{cvitems}
            \item {Monitor client's app running}
            \item {Support product development and customization}
        \end{cvitems}
    }

\cventry
    {Software Engineer(Junior)}
    {Emporia Digital Raya, Anabatic Technologies}
    {Serpong Tangerang, Indonesia}
    {Nov 2016 - Dec 2017}
    {
        \begin{cvitems}
            \item {Work in Agile running sprint every 2 weeks.}
            \item {Maintain Main site.}
            \item {Develop UI components using HTML, CSS, Javascript, and JSP.}
            \item {Develop web services in form of REST APIs, firebase push notif, mail services, authentication for mobile apps using PHP, Java and MySQL.}
            \item {Versioning and deployment.}
        \end{cvitems}
    }

\iffalse
\cventry
    {Internship}
    {Chevron Pacific Indonesia}
    {Duri Riau, Indonesia}
    {2015}
    {
        \begin{cvitems}
            \item {Internship under UTC-POD Team in IT Departement.}
            \item {Create simple web app using C\# ASP.Net to handle request for well surveys.}
        \end{cvitems}
    }
\fi

\end{cventries}
