\cvsection{Portfolio}
\begin{cventries}
\cventry
    {Implementing simple CRUD API services and CSV export/import using Go.}
    {TokoIjah}
    {\href{https://github.com/mfathirirhas/TokoIjah}{\faGithubSquare\acvHeaderIconSep\@Source}}
    {}
    {
        \begin{cvitems}
            \item {Using Gin Framework}
            \item {Using Gorm ORM}
            \item {Upload and download data in form of csv files}
        \end{cvitems}
    }

    
\cventry
    {Mini Image Processing using C\# with native windows form template and GDI+ Windows API.}
    {ImagePro}
    {\href{https://github.com/mfathirirhas/ImagePro}{\faGithubSquare\acvHeaderIconSep\@Source}}
    {}
    {
        \begin{cvitems}
            \item {Features: Grayscale, Invert Color, RGB Filtering, Sampling, Quantization, Geometry Manipulation, RGB Histogram, Convolution, Fast Fourier Transform, Smoothing(Mean,Median,Mode), Low and High Pass filter, Sharpening, Edge Detection, Black and White Thresholding, Region Growing, Dilation, Erosion, Open and Close.}
        \end{cvitems}
    }


\cventry
    {Simple blogging platform using Laravel(PHP).}
    {CodeBlog}
    {\href{https://github.com/mfathirirhas/codeblog}{\faGithubSquare\acvHeaderIconSep\@Source}}
    {}
    {
        \begin{cvitems}
            \item {Features include add post, edit post, delete post, view post, etc. Hosted on Azure with CI from bitbucket.}
            \item {Status: Discontinued}
        \end{cvitems}
    }


\cventry
    {College Final Project. A Native Windows form app using C\# to watermark image blindly using DWT and HMM techniques.}
    {Color Image Blind Watermarking}
    {\href{https://github.com/mfathirirhas/TugasAkhir1}{\faGithubSquare\acvHeaderIconSep\@Source}}
    {}
    {
        \begin{cvitems}
            \item {Features include watermark insertion, watermark extraction, attacks, and watermark detection.}
        \end{cvitems}
    }


\cventry
    {Simple Tetris game non-stop using C\# with native windows form.}
    {Unlimited Tetris}
    {\href{https://github.com/mfathirirhas/Game-Tetris}{\faGithubSquare\acvHeaderIconSep\@Source}}
    {}
    {
        \begin{cvitems}
            \item {\href{https://github.com/mfathirirhas/Game-Tetris/raw/master/DAA/bin/Release/DAA.exe}{Download}.}
        \end{cvitems}
    }


\cventry
    {Very simple CRUD web app using ASP.NET(C\#) for well survey request in Chevron UTC POD IT Department, Duri, Riau.}
    {Intern Web App}
    {\href{https://github.com/mfathirirhas/KPChevron2015}{\faGithubSquare\acvHeaderIconSep\@Source}}
    {}
    {
        \begin{cvitems}
            \item {\href{https://github.com/mfathirirhas/Game-Tetris/raw/master/DAA/bin/Release/DAA.exe}{Download}.}
        \end{cvitems}
    }


\cventry
    {Some programming questions and tests solved online from OpenKattis, Hackerrank, and some Euler Projects.}
    {Online Programming Questions}
    {\href{https://github.com/mfathirirhas/ProgrammingChallenges}{\faGithubSquare\acvHeaderIconSep\@Source}}
    {}
    {
        \begin{cvitems}
            \item {Solved using multiple languages with multiple difficulty.}
        \end{cvitems}
    }


\cventry
    {First project while working in Emporia Digital Raya written in Java using Spring MVC Maven Project.}
    {eksporaja.com}
    {}
    {}
    {
        \begin{cvitems}
            \item {A site for SME in Indonesia to Subscribe to Alibaba Global Gold Supplier(GGS) membership.}
            \item {Using Java Spring Framework for backend and HTML/CSS/Javascript and JSP for front-end.}
        \end{cvitems}
    }


\cventry
    {An Android and iOS app using PHP web services as backend and wordpress as back-office interface. Another project from Emporia to provide daily needs for buying foods online and paying another apartment bills online. You can order food online through nearest merchants registered in your clusters. You can also pay bills through this app(water, electricity, IPL, etc). Besides, there's also places directory to show you places/cities/areas and any unique spots in there(store,ATM machine, schools, etc).}
    {Infodaily}
    {}
    {}
    {
        \begin{cvitems}
            \item {Using PHP for backend, wordpress for backoffice, and mobile for frontend.}
        \end{cvitems}
    }
\end{cventries}
