\cvsection{Project}
\begin{cventries}
\cventry
    {Web app to handle request for well surveys. Internship project.}
    {Well Surveys Management}
    {Chevron Pacific Indonesia, Duri, Riau}
    {2015}
    {
        \begin{cvitems}
            \item {Created Auth and CRUD services to manage requests}
        \end{cvitems}
    }

    
\cventry
    {College Final Project}
    {Color Image Blind Watermarking using Discrete Wavelet Transform and Hidden Markov Model}
    {Telkom University, Bandung, Indonesia}
    {2015 - 2016}
    {
        \begin{cvitems}
            \item {Dekstop app created using C\#}
            \item {Implement blind watermarking using black and white image as information embedded into host image.}
            \item {Using Discrete Wavelet Transform for mapping embed scheme.}
            \item {Using Hidden Markov Model to detect clean or attacked watermark in host image.}
        \end{cvitems}
    }

\iffalse
\cventry
    {A Project while working in Emporia. Web app to subscribe to Alibaba GGS}
    {Eksporaja.com}
    {Emporia Digital, Serpong, Indonesia}
    {Nov 2016 - Mar 2017}
    {
        \begin{cvitems}
            \item {Web app created using Java, MySQL, Hibernate, and Tomcat for backend. HTML/CSS, Javascript, JSP for frontend}
            \item {Provide subscription to Alibaba GGS for SMEs in Indonesia.}
            \item {Provide payment gateway for Alibaba GGS Subscription using Doku.}
        \end{cvitems}
    }

\cventry
    {A Project while working in Emporia. B2C mobile app}
    {Infodaily}
    {Emporia Digital, Serpong, Indonesia}
    {Mar 2017 - February 2018}
    {
        \begin{cvitems}
            \item {A mobile app to provide B2C services(food, mart, billing payment) and places directory.}
            \item {Web services in form of REST APIs, Push notif, mail services, payment gateway, and authentication using PHP and AJAX .}
            \item {Back office created using wordpress.}
            \item {Mobile app created using Android and iOS}
        \end{cvitems}
    }
\fi
\end{cventries}
